---
title: "Epimodelling"
author: "Bence Gergely"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Epimodelling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## 1. What is Epimodelling?

<b>Epimodelling</b> is a tool to simulate and visualise data under different deterministic compartmental epidemiological models. It has two main functionality:

<ol>

<li>Manual mode</li>

<li>Interactive mode</li>

</ol>

In <b>Manual mode</b> you can choose model, solve the equations and visualise the results with few functions from R. In <b>Interactive mode</b> the user only calls the <i>EpiSimulator()</i> function which starts a Shiny web application.

## 3. How it's done in the Manual mode

Call the <i>epimodellR()</i> function and select the model. It will ask you to select the variable and parameter values in the console.

```{r model_setting,echo=FALSE}
library(Epimodelling)
mod <- epimodellR("SIR")

```

Next, you can call the <i>solve()</i> method in the following way:

```{r solve, echo=FALSE, eval = FALSE}

mod_solved <- solve(mod, delta_t = 0.01, days = 100)

```

Last, you can plot the results using the <i>plot</i> method:

```{r plot, echo=FALSE, eval = FALSE}

plot(mod_solved)

```

## 4. Interactive mode


Interactive mode is simple you just need to call:

```{r interactive, echo=FALSE, eval = FALSE}

EpiSimulator()

```

<i>That's all folks</i> 
